Gaussian Processes Autoregressive Models for Forecasting the Disturbance Storm Time Index

### 2016-06-07 swsc.tex
Added Simon's references

   \author{M. Chandorkar
          \inst{1}
          \and
          E. Camporeale\inst{1}
          \and 
          S. Wing \inst{2}
          }

@@

Auto-regressive models can be improved by including exogenous quantities that can help in improving predictions. It is well known that the solar wind and interplanetary magnetic field are important factors that influence the Earth's geomagnetic state (\citet{JGRA:JGRA11775}, \citet{Russell1974}, \citet{JGRA:JGRA17574}).

@@

\begin{thebibliography}{}

   \bibitem[Baker(1966)]{baker} Baker, N., Solar Evolution,
      in Stellar Evolution, ed.\ R. F. Stein and A. G. W. Cameron,
      Plenum, New York, 333, 1966.

   \bibitem[Balluch(1988)]{balluch} Balluch, M., A paper on something, 
      {\it Astron. Astrophys}, {\bf 200}, 58-63, 1988.

   \bibitem[Cox(1980)]{cox} Cox, J. P.,
      Theory of Stellar Pulsation,
      Princeton University Press, Princeton, 1980.

   \bibitem[Cox and Stewart(1969)]{cox69} Cox, A. N., and J. N. Stewart,
      Academia Nauk, {\it Scientific Information}, {\bf 15}, 1-11, 1969.

   \bibitem[Dumm and Kopf(2014)]{dummkopf} Dumm, Z., and Z. Kopf, A new self-inconsistent 
      core stability model, 
      {\it J. Space Weather Space Clim.}, {\bf 4}, A00, 2014, DOI: 10.1051/swsc/2014000,
      \url{http://dx.doi.org/10.1051/swsc/2014000}.

   \bibitem[Fool(2012)]{fool} Fool, X. Y., All earlier results are wrong, 
      {\it J. Space Weather Space Clim.}, {\bf 2}, A00, 2012, DOI: 10.1051/swsc/2012000,
      \url{http://dx.doi.org/10.1051/swsc/2012000}.

   \bibitem[Fou(2013)]{fou} Fou, Y. X., No earlier results were right, 
      {\it J. Space Weather Space Clim.}, {\bf 3}, A00, 2013, DOI: 10.1051/swsc/2013000,
      \url{http://dx.doi.org/10.1051/swsc/2013000}.

   \bibitem[Kr\"ugel et al.(1971)]{krugel71} Kr\"ugel, A. H., A. F. Davidsen, D. Tytler, and G. A. Kriss, 
      Summary of Project Achievements, Technical Report 08-11, 
      Fake Company, Nowherecity, Nowhereland, 1971.

   \bibitem[Mizuno(1980)]{mizuno} Mizuno, H., A further step backward in scientific understanding, 
      {\it Prog. Theor. Phys.}, {\bf 64}, 544-545, 1980.

   \bibitem[Tscharnuter(1987)]{tscharnuter} Tscharnuter, W. M., Who knows about astronomy?, 
      {\it Astron. Astrophys}, {\bf 188}, 55-57, 1987.

   \bibitem[Yorke(1980a)]{yorke80a} Yorke, H. W., A paper on nothing, 
      {\it Astron. Astrophys}, {\bf 86}, 286, 1980a.

   \bibitem[Yorke(1980b)]{yorke80b} Yorke, H. W., A paper on everything, 
      {\it Astron. Astrophys}, {\bf 86}, 291, 1980b.

>>>>

   \author{M. Chandorkar
          \inst{1}
          \and
          E. Camporeale\inst{1}
          \and 
          S. Wing \inst{1,2}
          }

@@

Auto-regressive models can be improved by including exogenous quantities that can help in improving predictions. $Dst$ gives a measure of ring currents, which are modulated by plasma sheet particle injections into the inner magnetosphere during sub-storms. Studies have shown that the substorm occurrence rate increases with solar wind velocity (high speed streams) (\citet{Kissinger2011}, \citet{Newell2016}). Prolonged southward interplanetary magnetic field (IMF) z-component ($B_z$) is needed for sub-storm to occur (\citet{McPherron1986}). An increase in the solar wind electric field, $VB_z$, can increase the dawn-dusk electric field in the magnetotail, which in turn determines the amount of plasma sheet particle that move to the inner magnetosphere (\citet{Friedel2001}). Therefore, our exogenous parameters consist of solar wind velocity, IMF $B_z$, and $VB_z$.

%It is well known that the solar wind and interplanetary magnetic field are important factors that influence the Earth's geomagnetic state (\citet{JGRA:JGRA11775}, \citet{Russell1974}, \citet{JGRA:JGRA17574}).

@@

\begin{thebibliography}{}
\end{thebibliography}
